Broom: Safe Region-Based Memory Management for Dataflow Programs

### 2015-11-06 paper/broom.tex
Edits.
Operational Semantics v1.

\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{stmaryrd}
\usepackage{comment}
\usepackage{float}
\usepackage{verbatimbox}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\usepackage[multiple]{footmisc}

@@

\newcommand{\redsto}[0]{\longrightarrow}

@@

\newcommand{\csolve}{{\sc CSolve}\xspace}

@@

\newcommand{\underlives}{\preceq}

@@

\newcommand{\rhoset}{\rhoenv}

@@

\newcommand{\lambdaexp}[3]{\lambda\inang{#1}(#2). #3}

@@

\newcommand{\invalidexn}{\C{InvalidOpnException}}

@@

@@

@@

@@

\newcommand{\lstml}{\lstset{ %
language=[Objective]Caml, % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code
keywordstyle=\color{Bittersweet},
% numbers=left,                   % where to put the line-numbers
numberstyle=\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
% frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
commentstyle=\itshape\color{MidnightBlue},
escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={foreach, do, done, not, : , /\\}
}}
\lstnewenvironment{codeml}
    { % \centering
			\lstml
      \lstset{mathescape=true}%
      \csname lst@setfirstlabel\endcsname}
    { %\centering
      \csname lst@savefirstlabel\endcsname}

@@

\input{type-inference}

>>>>

\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{stmaryrd}
\usepackage{comment}
\usepackage{float}
\usepackage{verbatimbox}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}

@@

\newcommand{\redsto}[3]{#1 \vdash #2 \longrightarrow #3}

@@

\newcommand{\csolve}{{\sc Csolve}\xspace}

@@

@@

\newcommand{\rhoset}{\Sigma}
\newcommand{\rhomap}{\Sigma}

@@

\newcommand{\lambdaexp}[4]{\lambda@#1\inang{#2}(#3). #4}

@@

\newcommand{\invalidexn}{\bot}

@@

\newcommand{\mbody}{{\sf mbody}}

@@

\newcommand{\shape}{{\sf shape}}

@@

\newcommand{\CLOSED}{\mathtt{C}}
\newcommand{\OPEN}{\mathtt{O}}
\newcommand{\XFERRED}{\mathtt{X}}
\newcommand{\transfer}{{\sf transfer}}

@@

@@
